### 2022-03-25 abstract.tex
Final Draft before defense

This dissertation focuses on how people search for information and how people
rely on this information to inform their health behaviors and develop social
norms. In academia and policy, the focus in research on 
information has most often focused on the information that is sent to 
consumers, seeing people as passive receivers of information. This
is otherwise known as a focus on the information 'push'. But, 
information is also intentionally sought out by individuals;
called information pull. My dissertation focuses on individuals as active agents 
in their search for information and how the information discovered through
these push and pull processes relates to the creation of social norms.

My first article tests the criterion validity of Google Search Trends as
an indicator of computer-mediated information search. I attempt to
validate Google Search Trends for use as indicators of attitudes, disease prevalence
and political preferences using five different validated data sources. 
My analysis revealed no correlation among any of the Google Trends tested and their
validated indicators. I demonstrate that there is no criterion validity of
Google Trends for the selected cases and social scientists will find no replacement for
high quality survey data with Google Trends. Instead, we must only use 
Google Trends to demonstrate interest or attention.

Knowing that Google Trends data only encompasses a small portion of the
information-seeking done by modern humans, my second article 
is motivated by the research question: How do computer-mediated or interpersonal 
information-seeking strategies vary across populations? Using original survey data
of 948 Americans, I investigate their experiences seeking out information about 
the COVID-19 vaccines. I investigate five distinct information seeking modalities, or methods of searching for information: 
personal connection, doctor, social networking site, online forum, and online search engine. 
% I find little evidence that online search is more utilized than
% seeking social support from personal network connections or health professionals
% as I had hypothesized based on uses and gratifications theory, 
% that media users are not passive consumers but instead actively choose
% media sources based on the satisfaction of their individual needs.
I find that different exposure points, the ways people first are exposed to 
information without searching for it, and information search modalities, the 
ways people intentionally search for information, hold real world consequences
through their associations with COVID-19 vaccination intentions and rates.
For example, receiving or seeking out information from a doctor increases 
 COVID-19 vaccination uptake while receiving information from a social 
 networking site was associated with lower odds of vaccination.

My final article takes a deeper dive into the formation of social norms
governing health behaviors in cases of extreme uncertainty, specifically using the cases of
 stay-at-home rates and vaccination rates as responses to public health
recommendations to mitigate the COVID-19 pandemic. Using the theories of associative diffusion
and the integrated theoretical framework of norms, I test models of behavioral adaption
to public health recommendations and patterns of complex contagion (the need for
repeated exposures to a something novel for it to diffuse) using linear
mixed effects models. My results show that complex contagion is a valid 
framework for the social contagion of new norms during COVID-19. 
However, I find an important novel moderating effect of signal discordance; 
if there is diversity in the information received by an ego, 
contagion is less likely to occur. This paper shows that
the contagion process is not fully understood without looking at the context
of each exposure to a contagion within the range of contagions one experiences.

>>>>

This dissertation focuses on how people search for information and how people
rely on this information to inform their health behaviors and develop social
norms. In academia and policy, the focus in research on information has most
often studied the information that is sent to consumers, seeing people as
passive receivers of information. This is otherwise known as information 'push'.
But, information is also intentionally sought out by individuals; called
information pull. My dissertation focuses on individuals as active agents in
their search for information and how the information discovered through these
push and pull processes relates to the creation of social norms.

My first article tests the criterion validity of Google Search Trends as an
indicator of computer-mediated information search. I attempt to validate Google
Search Trends for use as indicators of attitudes, disease prevalence and
political preferences using five different data sources. My analysis revealed no
correlation among any of the Google Trends tested and their validated
indicators. I demonstrate that there is no criterion validity of Google Trends
for the selected cases and social scientists will find no replacement for high
quality survey data with Google Trends. Instead, we must only use Google Trends
to demonstrate interest or attention.

Knowing that Google Trends data only encompasses a small portion of the
information-seeking done by modern humans, my second article is motivated by the
research question: How do computer-mediated or interpersonal information-seeking
strategies vary across populations? Using original survey data of 948 Americans,
I investigate their experiences seeking out information about COVID-19 vaccines.
I investigate five distinct information seeking modalities, or methods of
searching for information: personal connection, doctor, social networking site,
online forum, and online search engine. 
%I find little evidence that online search is more utilized than % seeking social support from personal network connections or health professionals % as I had hypothesized based on uses and gratifications theory, % that media users are not passive consumers but instead actively choose % media sources based on the satisfaction of their individual needs.
I find that different exposure points, the ways people first are exposed
to information without searching for it, and information search modalities hold
real world consequences through their associations with COVID-19 vaccination
intentions and rates. For example, I find that receiving or seeking out
information from a doctor increases COVID-19 vaccination uptake while receiving
information from a social networking site is associated with lower odds of
vaccination.

My final article takes a deeper dive into the formation of social norms
governing health behaviors in cases of extreme uncertainty. I specifically use
the cases of stay-at-home rates and vaccination rates as responses to public
health recommendations to mitigate the COVID-19 pandemic. Using the theories of
associative diffusion and the integrated theoretical framework of norms, I test
models of behavioral adaption to public health recommendations and patterns of
complex contagion (the need for repeated exposures to a something novel for it
to diffuse) using linear mixed effects models. My results show that complex
contagion is a valid framework for the social contagion of new norms during
COVID-19. However, I find an important novel moderating effect of signal
discordance; if there is diversity in the information received by an ego,
contagion is less likely to occur. This paper shows that the contagion process
is not fully understood without looking at the context of each exposure to a
contagion within the range of contagions one experiences.

### 2022-03-25 ch1.tex
Final Draft before defense

\subsection{Information Flow}
Humans have long been interested in how to persuade the masses. With the 
rise of democracy, the need of the powerful to persuade and appease the
masses dramatically increased. And for a while, behavioral scientists 
adopted really simplistic models of persuasion like the assumption
that the media influences behavior in a direct, unmediated, and 
all-powerful way (termed the hypodermic needle model in
\citet{bineham1988historical}) \citep{lasswellpropaganda}.

@@

Computational social science and social science disciplines are quick to adopt new
sources of digital trace data for use in academic research. In this article, I
examine the criterion validity of one of these new sources, Google Search Trends. I
validate how Google Trends can be used to demonstrate three different cases,
namely attitudes, disease prevalence and political preferences using five
different validated data sources. This paper asks, "How can we operationalize
Google Search Trends as a valid indicator for uses in social science research?"
I use Pearson and Repeated Measures Correlations between the Google Trends and
the validated indicators as well as multiple linear regression (for
cross-sectional datasets) and random intercept hierarchical linear models (for
longitudinal datasets) as additional tests of the data.

@@

% social epidemiology
I also make important contributions to social epidemiology through this
research with the use of health case studies for questions of sociological interest
across my three articles. Because of this, I 
contribute to the social epidemiological conversation on vaccine hesitancy,
health communication, and diffusion of high-risk health behaviors. While
all these areas are important to social epidemiology, there hold
potential important health implications for these contributions on
outside of the academy, covered in the first paragraphs of this chapter.

>>>>

\subsection{Information Flow}

Humans have long been interested in how to persuade the masses. With the rise of
democracy, the need of the powerful to persuade and appease the masses
dramatically increased. And for a while, behavioral scientists adopted really
simplistic models of persuasion like the assumption that the media influences
behavior in a direct, unmediated, and all-powerful way (termed the hypodermic
needle model in \citet{bineham1988historical}) \citep{lasswellpropaganda}.

@@

Computational social science and social science disciplines are quick to adopt
new sources of digital trace data for use in academic research. In this article,
I examine the criterion validity of one of these new sources, Google Search
Trends. I validate how Google Trends can be used to demonstrate three different
cases, namely attitudes, disease prevalence and political preferences using five
different validated data sources. This paper asks, "How can we operationalize
Google Search Trends as a valid indicator for uses in social science research?"
I use Pearson and Repeated Measures Correlations between the Google Trends and
the validated indicators as well as multiple linear regression (for
cross-sectional datasets) and fixed effect hierarchical linear models (for
longitudinal datasets) as additional tests of the data.

@@

% social epidemiology
I also make important contributions to social epidemiology through this research
with the use of health case studies for questions of sociological interest
across my three articles. Because of this, I contribute to the social
epidemiological conversation on vaccine hesitancy, health communication, and
diffusion of high-risk health behaviors. While all these areas are important to
social epidemiology, they hold potential important health implications for these
contributions on outside of the academy, covered in the first paragraphs of this
chapter.

### 2022-03-25 paper1.tex
Final Draft before defense

Computational social science and disciplines such as sociology and
political science are often quick to adopt new sources of digital 
trace data for use in academic research. 
In this article, I examine the validity of Google Search Trends 
as potential indicators of three different cases, namely attitudes, 
disease prevalence and political preferences using five
different validated data sources. I use Pearson and Repeated Measures Correlations 
between the Google Trends and the validated indicators as well as multiple linear regression
(for cross-sectional datasets) and random intercept hierarchical linear models
(for longitudinal datasets) as additional tests of the data. 
I fail to find correlation among any of the Google 
Trends tested and their validated indicators. While some Google Trends 
tested were significantly associated with the outcome in the regression models,
effects tended to be small and the total model interpretability remained low,
even when controlling for demographic variables. This article shows that there is no 
external validity of Google Trends for these uses and social scientists
will find no replacement for high quality survey data with Google Trends.

@@

New sources of digital trace data have led to vast possibilities for social science
research because they are bigger, cheaper, and already available 
\citep{kingEnsuringDataRichFuture2011,lazerComputationalSocialScience2009,salganikBitBitSocial2017}.
Digital trace data are the expansive volumes of information that are now available with the
introduction and widespread adoption of the internet and include sources such as  
social media sites, search data, blogs, adminstrative data on websites, the internet 
archives, etc. In short, digital trace data are the crumbs that are left as a person
peruses and interacts in digital spaces. Scholars have noted that these data provide
many new research avenues for social scientists because they are always on, non-reactive to
a researcher's observation, and very often captual social interactions and relationships,
but warn they can be Inaccessible, Non-Representative, and be prone to drifting due to
algorithmic confounding \citep{salganikBitBitSocial2017}.
Before overenthusiastically embracing these
sources and integrating them into our big data toolkits, social scientists must clearly establish
parameters under which these data sources are appropriate, 
and for which questions they are useful 
\citep{bailCulturalEnvironmentMeasuring2014, lazerParableGoogleFlu2014}. As
prior research outlined, the "quantity of data does not mean that one
can ignore foundational issues of measurement and construct validity and
reliability and dependencies among data" 
\citep[p. 1203]{lazerParableGoogleFlu2014}.

@@

\citet{cebrian_domenech22} emphasize in their research that there are some 
non-negligible issues with the measurement of Google Trends, pointing to 
errors within the purview of accuracy, completeness, consistency, and validity,
as outlined in \citet{KarrDataQuality}.  
% I know it is basic stats, but I would provide a footnote explaining each of your terms. Here, these line up with mainline stats but disciplines vary.
 \citet{cebrian_domenech22} point not only to 
meta issues like the lack of transparency into the sampling methods 
and population coverage, but they identify real differences 
in the data provided by the Google Trends API for the same 
researcher-entered query, pointing to likely internal process 
used by Google to sample their data to compute the trends.
These authors show that the variability of the results over time for the same query
can alter the results of analysis and forecasting significantly. While the 
issue of unreliability isn't unique to the Google Trends API, 
\citet{cebrian_domenech22} propose 
caution in the use of this digital trace data for other researchers until
further research can determine the root cause for the inaccuracies.
% Yes, big issue. But, it is also seen in machine learning, survey 
% administration, etc. I’d assume one solution for dealing with fiddly 
% output is to just sample repetedly and do some sort of average, 
% perhaps with a correction if the direction of the error is non random.

@@

To test how well Google Trends can be used to indicate other measures, 
I use various tests to validate the criterion validity of the trends. 
Criterion validity measures how well one measure, an operationalization of a 
specific construct, is able to predict a theoretical representation 
of the construct — the criterion. For this article, I employ 
concurrent criterion validity which looks at how Google Trends can
predict various criterions in the same time scale. 
I gathered geo-located social science data across multiple
sources to address the three areas of inquiry for this paper.  Table
\ref{tab:data-sources-table} outlines which data sources I use in this
project and which trends are matched to each source.

@@

\subsubsection{Google Trends}
This paper focuses on a triangulation of Google search trends \citep{googletrends}
with other sources of credible data.
Google trends portray the search frequency for specific search terms across
designated media markets areas (DMAs), a nonoverlapping aggregation of U.S.
counties to 210 media markets based on Nielsen's classification o "similar population clusters" \citep{dma_key}.
Raw data is on a scale from zero to one hundred, with one hundred being the maximum search
popularity out of all DMAs. When available, I use Google search topics to
measure trends as opposed to search terms. Search topics are a more robust
measurement than a single search term: topics are aggregations of the rates of
multiple, highly correlated search terms together into a cohesive topic done
by Google through it's Knowledge Graph product. For
example, while 'Beyoncé', 'Beyonce' and 'beyonce knowles' are all separate
search terms, 'Beyoncé Knowles' encompasses all of these into a single search
topic. Google Search Trends are only available cross-sectionally (a single 
period across a geography) or as time-series (a single geo-location across
time). To remedy this and build a longitudinal dataset of each search topic 
to match the longitudinal validated measures, I follow the method proposed 
in \citet[][p. 5]{park_etal}\footnote{This method involves building a dataset of unscaled cross-sectional values,
selecting a DMA to use to establish the rescaling ratio (I use 'Los Angeles
CA'), and then finding the time-series values for the one DMA. To find the
rescaling ratio for each week in the time-series, you divide the time-series
value for each week by the cross-sectional value for each week, resulting in a
rescaling vector to be used for all weeks in the dataset across geographies. To
rescale each longitudinal value, multiply the respective week's rescaling ratio
by the cross-sectional value. To validate this method, I compared the rescaled
longitudinal data against multiple samples of time-series data. For a more
in-depth explanation of this procedure, see \citet[p. 5]{park_etal}}. I interpolate 
missing datapoints in the longitudinal datasets using The Zoo package for R \citep{zoo}.

@@

I also use county-level suicide rates from the US Centers for Disease Control
and Prevention \citeyearpar{suic_data}. Data is grouped by year from 2010-2020. Raw death
rates are scaled by population size for each year and can be interpreted as the
death rate by suicide for every one thousand people. There are 34,683 total
cases, resulting from 10 observations of 3,147 counties. Missing data were interpolated using
\texttt{na.approx()} \citep{zoo}. Measures range from 0.034 to 53.254.

@@

As an additional criteria to evaluate the strength of the relationships, 
I employ multiple linear regression
(for cross-sectional datasets) and fixed effect hierarchical linear models
\citep{pinheiro_etal21} (for longitudinal datasets) to identify the strength of
relationships across locales. Multiple linear regression is appropriate because 
the cross-sectional data are non-nested which a continous outcome. Hierarchical
linear models are necessary to control for the between-subject variation 
in the longitudinal models. Fixed models are appropriate because 
they extract the between group-differences from the model to allow the reader to 
focus on the overall effects of each variable. 
In these models, include location metadata like county population size,
broadband rates, and median income to adjust for potentially
confounded relationships between Google search Trends and credible
indicators. Identifying these possible confounded relationships may help to
explain why some articles find relationships between the trends and outcomes
while others did not.
For linear regression models, I normalize independent
variables so that each variable across each model is on the same scale and can be compared. 
In other words, variables have been centered and scaled to have a mean of zero and
standard deviation of one. Results of these models are in Tables \ref{tab:vacc_hes_analysis} through \ref{tab:pres_2020_analysis}.

@@

In addition to attitudinal measures, I attempt to validate Google Trends for
uses in the measurements of health indicators. The first indicator I assess is
COVID-19 case rates from 2020 through 2021. The Pearson correlation results
indicate negligible to weak relationships between the search terms and the
actual case rates across time and place. The repeated measures correlation
coefficient, a more reliable and less biased measure for longitudinal
correlations, reveals similarly weak results with a maximum correlation of 0.32
between 'smell loss' and rates of COVID-19. To further investigate the relationship, I
include the three trends in random intercept hierarchical linear models. Model 1
of Table \ref{tab:covid_analysis} indicates that the trends themselves are able
to explain about 20\% of the variation in COVID-19 rates ($r^2$ = 0.201). Few
of the demographic variables influence COVID-19 rates in models 2 or 3,
though there is some suppression for median income, unemployment rates,
and population density. Model 3 has an $r^2$ of 0.200. I conclude that the
Google Trends are slightly related to COVID-19 rates, but that this relationship
is weak, and we should not attempt to use Google Trends as an indicator of actual
health outcomes.

@@

Another health outcome I test is county suicide rates. As with previous cases,
there is only negligible correlation between actual suicide rates and Google
Search Trends, not exceeding 0.0845. In the more accurate repeated measures
correlation coefficient we see a maximum of 0.142 correlation, remaining
negligible. I introduce these trends into a random intercept model to control
for inter-group variation over time in Table \ref{tab:suicide_analysis}. While
table \ref{tab:suicide_analysis} model 1 reveals a statistically significant relationship
between suicide hotline trends and suicide rates, the effect is small, and the
entire model only has an $r^2$ of 0.058. Adding in demographic features in model
2 improves the $r^2$ to 0.56. In model 3, the inclusion of Google Trends
decreases the overall amount of suicide rate variance explained
compared to model 2. These analyses lead me to conclude that Google Search
Trends should not be used by researchers as indicators of suicide rates or intentions.

>>>>

Computational social science and disciplines such as sociology and political
science are often quick to adopt new sources of digital trace data for use in
academic research. In this article, I examine the criterion validity of Google
Search Trends as potential indicators of three different cases, namely
attitudes, disease prevalence and political preferences using five different
validated data sources. I use Pearson and Repeated Measures Correlations between
the Google Trends and the validated indicators as well as multiple linear
regression (for cross-sectional datasets) and fixed effect hierarchical linear
models (for longitudinal datasets) as additional tests of the data. I find no
correlation among any of the Google Trends tested and their validated
indicators. While some Google Trends tested were significantly associated with
the outcome in the regression models, effects tended to be small and the total
model interpretability remained low, even when controlling for demographic
variables. This article shows that there is no criterion validity of Google
Trends for these uses and social scientists are not able to use Google Trends as
a stand-in for high quality survey data.

@@

New sources of digital trace data have led to vast possibilities for social
science research because they are bigger, cheaper, and already available
\citep{kingEnsuringDataRichFuture2011,lazerComputationalSocialScience2009,salganikBitBitSocial2017}.
Digital trace data are the expansive volumes of information that are now
available with the introduction and widespread adoption of the internet and
include sources such as social media sites, search data, blogs, administrative
data on websites, the internet archives, etc. In short, digital trace data are
the crumbs that are left as a person peruses and interacts in digital spaces.
Scholars have noted that these data provide many new research avenues for social
scientists because they are always on, non-reactive to a researcher's
observation, and very often capture social interactions and relationships, but
warn they can be inaccessible, non-representative, and be prone to drifting due
to algorithmic confounding\citep{salganikBitBitSocial2017}. Before
overenthusiastically embracing these sources and integrating them into our big
data toolkits, social scientists must clearly establish parameters under which
these data sources are appropriate, and for which questions they are useful
\citep{bailCulturalEnvironmentMeasuring2014, lazerParableGoogleFlu2014}. As
prior research outlined, the "quantity of data does not mean that one can ignore
foundational issues of measurement and construct validity and reliability and
dependencies among data" \citep[p. 1203]{lazerParableGoogleFlu2014}.

@@

\citet{cebrian_domenech22} emphasize in their research that there are some
non-negligible issues with the measurement of Google Trends, pointing to errors
within the purview of accuracy, completeness, consistency, and validity, as
outlined in \citet{KarrDataQuality}. % I know it is basic stats, but I would
provide a footnote explaining each of your terms. Here, these line up with
mainline stats but disciplines vary. \citet{cebrian_domenech22} point not only
to meta issues like the lack of transparency into the sampling methods and
population coverage, but they identify real differences in the data provided by
the Google Trends API for the same researcher-entered query, pointing to likely
internal process used by Google to sample their data to compute the trends.
These authors show that the variability of the results over time for the same
query can alter the results of analysis and forecasting significantly. While the
issue of unreliability isn't unique to the Google Trends API,
\citet{cebrian_domenech22} propose caution in the use of this digital trace data
for other researchers until further research can determine the root cause for
the inaccuracies.
% Yes, big issue. But, it is also seen in machine learning, survey 
% administration, etc. I’d assume one solution for dealing with fiddly 
% output is to just sample repeatedly and do some sort of average, 
% perhaps with a correction if the direction of the error is non random.

@@

To test how well Google Trends can be used to indicate other measures, I use
various tests to validate the criterion validity of the trends. Criterion
validity measures how well one measure, an operationalization of a specific
construct, is able to predict a theoretical representation of the construct —
the criterion. For this article, I employ concurrent criterion validity which
looks at how Google Trends can predict various criterions in the same time
scale. I gathered geolocated social science data across multiple sources to
address the three areas of inquiry for this paper.  Table
\ref{tab:data-sources-table} outlines which data sources I use in this project
and which trends are matched to each source.

@@

\subsubsection{Google Trends}
This paper focuses on a triangulation of Google search trends
\citep{googletrends} with other sources of credible data. Google trends portray
the search frequency for specific search terms across designated media markets
areas (DMAs), a nonoverlapping aggregation of U.S. counties to 210 media markets
based on Nielsen's classification o "similar population clusters"
\citep{dma_key}. Raw data is on a scale from zero to one hundred, with one
hundred being the maximum search popularity out of all DMAs. When available, I
use Google search topics to measure trends as opposed to search terms. Search
topics are a more robust measurement than a single search term: topics are
aggregations of the rates of multiple, highly correlated search terms together
into a cohesive topic done by Google through it's Knowledge Graph product. For
example, while 'Beyoncé', 'Beyonce' and 'beyonce knowles' are all separate
search terms, 'Beyoncé Knowles' encompasses all of these into a single search
topic. Google Search Trends are only available cross-sectionally (a single
period across a geography) or as time-series (a single geo-location across
time). To remedy this and build a longitudinal dataset of each search topic to
match the longitudinal validated measures, I follow the method proposed in
\citet[][p. 5]{park_etal}\footnote{This method involves building a dataset of
unscaled cross-sectional values, selecting a DMA to use to establish the
rescaling ratio (I use 'Los Angeles CA'), and then finding the time-series
values for the one DMA. To find the rescaling ratio for each week in the
time-series, you divide the time-series value for each week by the
cross-sectional value for each week, resulting in a rescaling vector to be used
for all weeks in the dataset across geographies. To rescale each longitudinal
value, multiply the respective week's rescaling ratio by the cross-sectional
value. To validate this method, I compared the rescaled longitudinal data
against multiple samples of time-series data. For a more in-depth explanation of
this procedure, see \citet[p. 5]{park_etal}}. I interpolate missing data points
in the longitudinal datasets using The Zoo package for R \citep{zoo}.

@@

I also use county-level suicide rates from the US Centers for Disease Control
and Prevention \citeyearpar{suic_data}. Data is grouped by year from 2010-2020.
Raw death rates are scaled by population size for each year and can be
interpreted as the death rate by suicide for every one thousand people. There
are 34,683 total cases, resulting from 10 observations of 3,147 counties.
Missing data were interpolated using \citet{zoo}. Measures range from 0.034 to
53.254.

@@

As an additional criteria to evaluate the strength of the relationships, I
employ multiple linear regression (for cross-sectional datasets) and fixed
effect hierarchical linear models \citep{pinheiro_etal21} (for longitudinal
datasets) to identify the strength of relationships across locales. Multiple
linear regression is appropriate because the cross-sectional data are non-nested
which a continuous outcome. Hierarchical linear models are necessary to control
for the between-subject variation in the longitudinal models. Fixed models are
appropriate because they extract the between group-differences from the model to
allow the reader to focus on the overall effects of each variable. In these
models, include location metadata like county population size, broadband rates,
and median income to adjust for potentially confounded relationships between
Google search Trends and credible indicators. Identifying these possible
confounded relationships may help to explain why some articles find
relationships between the trends and outcomes while others did not. For linear
regression models, I normalize independent variables so that each variable
across each model is on the same scale and can be compared. In other words,
variables have been centered and scaled to have a mean of zero and standard
deviation of one. Results of these models are in Tables
\ref{tab:vacc_hes_analysis} through \ref{tab:pres_2020_analysis}.

@@

In addition to attitudinal measures, I attempt to validate Google Trends for
uses in the measurements of health indicators. The first indicator I assess is
COVID-19 case rates from 2020 through 2021. The Pearson correlation results
indicate negligible to weak relationships between the search terms and the
actual case rates across time and place. The repeated measures correlation
coefficient, a more reliable and less biased measure for longitudinal
correlations, reveals similarly weak results with a maximum correlation of 0.32
between 'smell loss' and rates of COVID-19. To further investigate the
relationship, I include the three trends in fixed effect hierarchical linear
models. Model 1 of Table \ref{tab:covid_analysis} indicates that the trends
themselves are able to explain about 20\% of the variation in COVID-19 rates
($r^2$ = 0.201). Few of the demographic variables influence COVID-19 rates in
models 2 or 3, though there is some suppression for median income, unemployment
rates, and population density. Model 3 has an $r^2$ of 0.200. I conclude that
the Google Trends are slightly related to COVID-19 rates, but that this
relationship is weak, and we should not attempt to use Google Trends as an
indicator of actual health outcomes.

@@

Another health outcome I test is county suicide rates. As with previous cases,
there is only negligible correlation between actual suicide rates and Google
Search Trends, not exceeding 0.0845. In the more accurate repeated measures
correlation coefficient we see a maximum of 0.142 correlation, remaining
negligible. I introduce these trends into a fixed effect model to control for
inter-group variation over time in Table \ref{tab:suicide_analysis}. While table
\ref{tab:suicide_analysis} model 1 reveals a statistically significant
relationship between suicide hotline trends and suicide rates, the effect is
small, and the entire model only has an $r^2$ of 0.058. Adding in demographic
features in model 2 improves the $r^2$ to 0.56. In model 3, the inclusion of
Google Trends decreases the overall amount of suicide rate variance explained
compared to model 2. These analyses lead me to conclude that Google Search
Trends should not be used by researchers as indicators of suicide rates or
intentions.

### 2022-03-25 paper2.tex
Final Draft before defense

Previous research has greatly failed to distinguish between the activation of
information seeking behaviors online and offline. Using theories of 1) social
support and 2) uses and gratifications theory I investigate the factors associated
with each modality type when on information seeking modality: personal connection,
doctor, social networking site, online forum, and online search engine. Using
novel survey data of 948 Americans and their experience seeking out
information about the COVID-19 vaccines, I find little evidence that online
search is more utilized than seeking social support from personal network
connections or health professionals. I find evidence that the modalities queried
in this survey are conceptually different and that the utilization of different
modalities varies by demography and information sources. Finally, I find that
different sources of information exposure and information search modalities hold real
world consequences through their associations with COVID-19 vaccination rates
and intentions, as information from a doctor increased the COVID-19 vaccination
uptake while receiving information from a social networking site like Facebook
or Twitter was associated with lower odds of vaccination.

@@

The lack of research in which modalities are likely to be chosen when an
individual faces a need for information makes it difficult for policy makers to
propose effective information campaigns that promote the health and wellbeing of
individuals in our society. Even outside of the misinformation literature, much
of the research conducted in social networks and communication focus on senders,
influencers, and persuasion strategies 
\citep{mertonManifestLatentFunctions1968, katzPersonalInfluencePart1955, lazarsfeldPeopleChoice1944},
rather than on “the receiver as an active information seeker and processor." 
\citep{johnsonComprehensiveModelCancerRelated1993}
\citep[for an exception, see]{eysenbach09}.

@@

\hypertarget{information-search}{%
\subsection{Information Search}\label{information-search}}

Active, directed searching by individuals to obtain information is sparsely
discussed in the sociological literature. Pejtersen \citet{pejtersenDesignComputeraidedUsersystem1984}, a scholar
of library and information science, theorized that there are five strategies for
searching for information: browsing, analytical, empirical, known site, and similarity. 
The most common strategy is browsing, where people
follow leads based on associations without premeditation. Another strategy is
analytical, which includes an explicit consideration of all facets of the
question to guide a search. The empirical method guides the search based on
tactics that were successful in past research. The known site strategy is to go
to the direct source of the information if known. And finally, the similarity
method is to find information based on another similar question that already has
an answer. These five strategies vary in their demands for prior knowledge,
cognitive processing, memory, and time spent. While this theory is aimed at
finding information in a library setting, scholars have extended the theory to
other fields and validated the framework
\citep{fidelHumanInformationInteraction2012}; the frame is a useful beginning point
for my theories of information search through network activation or through
computer-mediated communication.

@@

Adapting these facets of UGT and social support to my own case, I theorize that
online search allows for increased anonymity, a lowered social cost, and the
potential avoidance of embarrassment and other negative social interactions,
especially in the case on search engines. \citet{rainsCopingIllnessDigitally2018}
finds that patients tend to search for
technical information about an illness online but they then turn to their social
network for experiential information from others facing similar circumstances in
the case of cancer. The type of information sought is therefore important.
If specific expertise on a specific topic is desired by a searcher, they may
reach out to personal connections that they see as expert such as a doctor, or
if an individual distrusts the medical establishment, they may be more likely to
activate informational support among their social network or turn to online
groups that validate their worldview \citep{bogersHowSocialAre2014}. Finally, UGT and
Brasher's definition of social support \citeyearpar{brashersInformationSeekingAvoiding2002}
help us to theorize that the psychosocial needs like identity management or relational
maintenance of an individual may influence their chosen information search modality: 
when the informational need is related to forming and deepening social ties search 
is likely to be done from network ties.

@@

\hypertarget{research-methodology}{%
\section{Research Methodology}\label{research-methodology}}

@@

The survey took an average of 24.48 minutes with a standard deviation of 13.23 minutes.
The shortest valid survey took 3.75 minutes and the longest took 111.08 minutes.
Participants received \$6.00 in compensation for their participation in the survey
\footnote{All funding for this survey was provided by a Grant awarded to Kelsey E. 
Gonzalez and Nicolas Legewie by the Summer Institute in Computational Social Science
and the Russell Sage Foundation.}. The survey consisted of two main parts. The
first portion of the survey is a replication of they survey conducted by 
\citet{smallSomeoneTalk2017}. In this section, we expand Small's research on 
support activation by segregating weak-tie social support into instrumental, 
emotional, and informational categories \citep[see][]{houseStructuresProcessesSocial1988}.
The second part of the survey focuses on network resource activation and 
information seeking behaviors of individuals regarding COVID-19 vaccinations
for this paper.

@@

\hypertarget{vaccination-outlook}{%
\subsubsection{Vaccination Outlook}\label{vaccination-outlook}}

@@

I find that indeed the most common modalities are 
asking a doctor, asking a friend, and asking a search engine which confirms
Hypthesis \ref{hyp:drgooglefriend}. However, because the modalities 95\% confidence intervals 
in Table \ref{tab:table-1-ind}
are overlapping, I fail to find evidence for Hypothesis \ref{hyp:online-vs-network},
that using an online search engine was more commonplace than asking a friend.

>>>>

Previous research has greatly failed to distinguish between the activation of
information seeking behaviors online and offline. Using theories of 1) social
support and 2) uses and gratifications theory I investigate the factors
associated with each type of information search: 
personal connection, doctor, social networking site, online forum, and online
search engine. Using novel survey data of 948 Americans and their experience
seeking out information about the COVID-19 vaccines, I find little evidence that
online search is more utilized than seeking social support from personal network
connections or health professionals. I find evidence that the modalities queried
in this survey are conceptually different and that the utilization of different
modalities varies by demography and information exposure points, where
individuals are provided with information without seeking it. Finally, I find that
different sources of information exposure and information search modalities hold
real world consequences through their associations with COVID-19 vaccination
intentions and rates, as information from a doctor increases COVID-19
vaccination uptake while receiving information from a social networking site
is associated with lower odds of vaccination.

@@

The lack of research in which modalities are likely to be chosen when an
individual faces a need for information makes it difficult for policy makers to
propose effective information campaigns that promote the health and well-being
of individuals in our society. Even outside of the misinformation literature,
much of the research conducted in social networks and communication focus on
senders, influencers, and persuasion strategies
\citep{mertonManifestLatentFunctions1968, katzPersonalInfluencePart1955,
lazarsfeldPeopleChoice1944}, rather than on “the receiver as an active
information seeker and processor."
\citep{johnsonComprehensiveModelCancerRelated1993} \citep[for an exception,
see]{eysenbach09}.

@@

\hypertarget{information-search}{\subsection{Information Search}\label{information-search}}

Active, directed searching by individuals to obtain information is sparsely
discussed in the sociological literature.
\citet{pejtersenDesignComputeraidedUsersystem1984}, a scholar of library and
information science, theorized that there are five strategies for searching for
information: browsing, analytical, empirical, known site, and similarity. The
most common strategy is browsing, where people follow leads based on
associations without premeditation. Another strategy is analytical, which
includes an explicit consideration of all facets of the question to guide a
search. The empirical method guides the search based on tactics that were
successful in past research. The known site strategy is to go to the direct
source of the information if known. And finally, the similarity method is to
find information based on another similar question that already has an answer.
These five strategies vary in their demands for prior knowledge, cognitive
processing, memory, and time spent. While this theory is aimed at finding
information in a library setting, scholars have extended the theory to other
fields and validated the framework \citep{fidelHumanInformationInteraction2012};
the frame is a useful beginning point for my theories of information search
through network activation or through computer-mediated communication.

@@

Adapting these facets of UGT and social support to my own case, I theorize that
online search allows for increased anonymity, a lowered social cost, and the
potential avoidance of embarrassment and other negative social interactions,
especially in the case on search engines.
\citet{rainsCopingIllnessDigitally2018} finds that patients tend to search for
technical information about an illness online but they then turn to their social
network for experiential information from others facing similar circumstances in
the case of cancer. The type of information sought is therefore important. If
specific expertise on a specific topic is desired by a searcher, they may reach
out to personal connections that they see as expert such as a doctor, or if an
individual distrusts the medical establishment, they may be more likely to
activate informational support among their social network or turn to online
groups that validate their worldview \citep{bogersHowSocialAre2014}. Finally,
UGT and Brasher's definition of social support
\citeyearpar{brashersInformationSeekingAvoiding2002} help us to theorize that
the psychosocial needs like identity management or relational maintenance of an
individual may influence the chosen information search modality: when the
informational need is related to forming and deepening social ties search is
likely to be done from network ties.

@@

\hypertarget{research-methodology}{\section{Research Methodology}\label{research-methodology}}

@@

The survey took an average of 24.48 minutes with a standard deviation of 13.23
minutes. The shortest valid survey took 3.75 minutes and the longest took 111.08
minutes. Participants received \$6.00 in compensation for their participation in
the survey \footnote{All funding for this survey was provided by a Grant from
the Summer Institute in Computational Social Science and the Russell Sage
Foundation.}. The survey consisted of two main parts. The first portion of the
survey is a replication of they survey conducted by
\citet{smallSomeoneTalk2017}. In this section, we expand Small's research on
support activation by segregating weak-tie social support into instrumental,
emotional, and informational categories
\citep[see][]{houseStructuresProcessesSocial1988}. The second part of the survey
focuses on network resource activation and information seeking behaviors of
individuals regarding COVID-19 vaccinations for this paper.

@@

\hypertarget{vaccination-outlook}{\subsubsection{Vaccination Outlook}\label{vaccination-outlook}}

@@

I find that indeed the most common modalities are asking a doctor, asking a
friend, and asking a search engine which confirms Hypothesis
\ref{hyp:drgooglefriend}. However, because the modalities 95\% confidence
intervals in Table \ref{tab:table-1-ind} are overlapping, I fail to find
evidence for Hypothesis \ref{hyp:online-vs-network}, that using an online search
engine was more commonplace than asking a friend.
